### 2011-04-14 Text/paper.tex
Added interface velocities. When work with vtk don't use twodimensional images.

For simplicity, the periodic boundary conditions are applied. Thus, the bubble train is simulated.
To avoid the mutual influence of bubbles on each other the channel length was chosen as $15
H_{\mathrm{eff}}$. Periodic boundary conditions imply as well that the fluid is accelerated by a
body force in the framework of the LBM but not with the pressure difference. Therefore, we can not
address simulations with upward and downward flows \cite{cerro-bubble-train}. It is assumed that
the gravity effects are negligible and the flow is in the horizontal direction driven by the body
force. 
\begin{figure}[ht]
\includegraphics*[bb=153 610 405 717,width=\textwidth]{Figures/benchmark_classical.eps} 
\caption{The classical benchmark. The semiinfinite gas bubble
propagates through the liquid media. \label{fig:classical:benchmark}}
\end{figure}[ht]
\begin{figure}
\includegraphics*[bb=152 470 410 713,width=\textwidth]{Figures/benchmark_lbm.eps}
\caption{The classical benchmark. The semiinfinite gas bubble
propagates through the liquid media. \label{fig:lbm:benchmark}}
\end{figure}

@@

The bubble velocity is the velocity of the interface. One can see it with ...

@@

\section{Velocity pattern}
We examined two different velocity patterns to identify change of pattern. Two capillaries numbers
were taken below and above the numbers indicated in Table \ref{table:recirculation:data}, as
$Ca=0.36$ and $Ca=0.88$.Velocity streamlines are
indicated in Fig. \ref{fig:streamlines:pattern}. One can see that the vortex indicated in
Fig.\ref{fig:heil:recirculating} doesn't appear in present calculations. This fact can be
explained because the simulation is carried our for the binary-liquid case but not free-surface
interface presented in the classical Bretherton problem. In the latter case the void phase pushes
the liquid towards the walls. In the present simulation there is no a void phase. Then the
streamlines have the ability to go through the interface and we exactly see this situation occuring.
\begin{figure}[ht]
\includegraphics[width=0.97\textwidth]{Figures/streamlines_ca036.eps}\\
\includegraphics[width=0.97\textwidth]{Figures/streamlines_ca088.eps}
\caption{Streamlines for $Ca=0.36$ and $Ca=0.88$. One can see that there are no vortexes created
before the bubble. It can be explained by the fact that the binary-liquid model is simulated
instead of free-surface interface gas air finger flow.\label{fig:streamlines:pattern}}
\end{figure}

>>>>

For simplicity, the periodic boundary conditions are applied. Thus, the bubble train is simulated.
To avoid the mutual influence of bubbles on each other the channel length was chosen as $15
H_{\mathrm{eff}}$. Periodic boundary conditions imply as well that the fluid is accelerated by a
body force in the framework of the LBM but not with the pressure difference. Therefore, we can not
address simulations with upward and downward flows \cite{cerro-bubble-train}. It is assumed that
the gravity effects are negligible and the flow is in the horizontal direction driven by the body
force. 
\begin{figure}[!]
\includegraphics*[bb=153 610 405 717,width=\textwidth]{Figures/benchmark_classical.eps} 
\caption{The classical benchmark. The semiinfinite gas bubble
propagates through the liquid media. \label{fig:classical:benchmark}}
\end{figure}[!]
\begin{figure}
\includegraphics*[bb=152 470 410 713,width=\textwidth]{Figures/benchmark_lbm.eps}
\caption{The classical benchmark. The semiinfinite gas bubble
propagates through the liquid media. \label{fig:lbm:benchmark}}
\end{figure}

@@

To further examine the steady-state the velocity in the streamwise direction is plotted. The values
of the velocity are taken on the contour where phase values are taken as $\phi=0$. This corresponds
 to the bubble interface. One can see the contour plot and the corressponing streamwise velocity
component in Fig. \ref{fig:velocity:contour}. The crossection is a plane $x=0$, where $x$ points
towards the reader, $z$ is the streamwise direction. As far as fluxes inside the bubble has
clockwise and counterclockwise directions, see Section \ref{sec:velocity}, one needs to thoroughly
examine only the points corresponding to the front and the rear bubble tips. If one finds it equal
to each other, then it's exactly the velocity with which the bubble propagates in the microchannel. 
\begin{figure}[h!]
\includegraphics[width=\textwidth]{Figures/velocity_interface_contour.eps}\\
\includegraphics[width=\textwidth]{Figures/velocity_interface_values.eps}\\
\caption{The bubble shape and the corresponding streamwise velocities taken on the bubble
interface. Directions $y$ and $z$ are scaled to the half of the channel
$H_{\mathrm{eff}}/2$. One can see that the bubble front and rear tips are propagating with the
same velocities, which is actually the bubble velocity. For more details on velocity patterns
see Section \ref{sec:velocity}. \label{fig:velocity:contour}}
\end{figure}

@@

\section{Velocity pattern}
\label{sec:velocity}
We examined two different velocity patterns to identify change of pattern. Two capillaries numbers
were taken below and above the numbers indicated in Table \ref{table:recirculation:data}, as
$Ca=0.36$ and $Ca=0.88$.Velocity streamlines are
indicated in Fig. \ref{fig:streamlines:pattern}. One can see that the vortex indicated in
Fig.\ref{fig:heil:recirculating} doesn't appear in present calculations. This fact can be
explained because the simulation is carried our for the binary-liquid case but not free-surface
interface presented in the classical Bretherton problem. In the latter case the void phase pushes
the liquid towards the walls. In the present simulation there is no a void phase. Then the
streamlines have the ability to go through the interface and we exactly see this situation occuring.
\begin{figure}[ht]
\includegraphics[width=0.97\textwidth]{Figures/streamlines_ca036.eps}\\
\includegraphics[width=0.97\textwidth]{Figures/streamlines_ca088.eps}
\caption{Streamlines for $Ca=0.36$ and $Ca=0.88$. One can see that there are no vortexes created
before the bubble. It can be explained by the fact that the binary-liquid model is simulated
instead of free-surface interface gas air finger flow.\label{fig:streamlines:pattern}}
\end{figure}
